Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
update od approach => approaches

with $K^{c(uv)}$ being the slice of $K^{c}$ containing the pairwise similarities between the centroids sets $c^u$ and $c^v$ belonging to the scenes $s_u$ and $s_v$ respectively. As suggested in \cite{pele2009fast}, we set the $\alpha$ parameter to one.\\

@@

Different sets of parameters were tested to compute the MFFCs. We here report only the results for the best setting, which is similar to the one used by the winners of the previous DCASE 2013 challenge \cite{roma2013}. 40 MFCCs (including the first energy coefficient) are computed for windows of 50ms and hops of 25ms, with a limited frequency range going from $27.5$Hz to $1000$Hz. This setting gives us 600 feature vectors per scenes. It has been reported that classifying the full set of frames directly may not be the best approach \cite{rakotomamonjy2015histogram}. In order to reduce the data dimensionality, a pooling step is performed on the MFCCs vectors: each set of MFCCs vectors is dividing into $n$ non-overlapping $t$-seconds long slices. Each $n$ MFCC slices is then averaged over time. As the \emph{ob} approach involves a clustering step, it is desirable to ensure that each scene is described by circa the same number of vectors,for both the temporal-scattering and the MFCCs, prior to running the clustering. Thus, $t$ is set to 250ms, which gives us 120 MFCCs vectors per scenes.

@@

The influence of the temporal-scattering transform and the \emph{ob} are assessed in an unsupervised setting (\emph{i.e.} ASS) and in a supervised setting (\emph{i.e.} ASC).

For the ASS setting, evaluation is performed on the private dataset of the DCASE 2013 challenge. The metric used is the precision at rank $k$ ($p@k$), which is the  average  number  of  items  of  the  same  class among the $k$ closest items averaged for all possible seed items. The $p@k$ is computed for $k=[1,\ldots,9]$. Note that a $p@1$ is equivalent to an accuracy computed based on the labels of the 1st nearest neighbors of the items to classify. For each experimental setting, we report the results for the set of parameters, \emph{i.e.} the number of clusters $m$ for the \emph{ob} approach and the scaling parameters $N$ of the RBF kernels (see Eq. \ref{eq:kc}) giving the best $p@9$.

@@

The \emph{ob} approach is compared to commonly used approaches using an early integration strategy (\emph{ei}) for the ASS setting, and both an early and a late integration (\emph{li}) strategy for the ASC setting (see Section \ref{sec:eili}).

>>>>

with $K^{c(uv)}$ being the slice of $K^{c}$ containing the pairwise similarities between the centroids sets $c^u$ and $c^v$ of the scenes $s_u$ and $s_v$ respectively. As suggested in \cite{pele2009fast}, we set the $\alpha$ parameter to one.\\

@@

Different sets of parameters were tested to compute the MFFCs. We here report only the results for the best setting, which is similar to the one used by the winners of the previous DCASE 2013 challenge \cite{roma2013}. 40 MFCCs (including the first energy coefficient) are computed for windows of 50ms and hops of 25ms, with a limited frequency range going from $27.5$Hz to $1000$Hz. This setting gives us 600 feature vectors per scenes. It has been reported that classifying the full set of frames directly may not be the best approach \cite{rakotomamonjy2015histogram}. In order to reduce the data dimensionality, a pooling step is performed on the MFCCs vectors: each set of MFCCs vectors is dividing into $n$ non-overlapping $t$-seconds long slices. Each $n$ MFCC slices is then averaged over time. As the \emph{ob} approaches involve a clustering step, it is desirable to ensure that each scene is described by circa the same number of vectors,for both the temporal-scattering and the MFCCs, prior to running the clustering. Thus, $t$ is set to 250ms, which gives us 120 MFCCs vectors per scenes.

@@

The influence of the temporal-scattering transform and the \emph{ob} approaches are assessed in an unsupervised setting (\emph{i.e.} ASS) and in a supervised setting (\emph{i.e.} ASC).

For the ASS setting, evaluation is performed on the private dataset of the DCASE 2013 challenge. The metric used is the precision at rank $k$ ($p@k$), which is the  average  number  of  items  of  the  same  class among the $k$ closest items averaged for all possible seed items. The $p@k$ is computed for $k=[1,\ldots,9]$. Note that a $p@1$ is equivalent to an accuracy computed based on the labels of the 1st nearest neighbors of the items to classify. For each experimental setting, we report the results for the set of parameters, \emph{i.e.} the number of clusters $m$ for the \emph{ob} approaches and the scaling parameters $N$ of the RBF kernels (see Eq. \ref{eq:kc}) giving the best $p@9$.

@@

The \emph{ob} approaches are compared to commonly used approaches using an early integration strategy (\emph{ei}) for the ASS setting, and both an early and a late integration (\emph{li}) strategy for the ASC setting (see Section \ref{sec:eili}).
